Travel Survey and Census population for Bogota

### 2023-03-29 code/synthetic_population/bogota_synth_pop.qmd
Move takeaway message to the front. Ref #128
Rename household weights as individual weights. Ref #128

| Sex    | Population (N) | Percent (%) | Travel Survey Population (N) | Percent (%) |
|--------|----------------|-------------|------------------------------|-------------|
| Female | 2,996,444      | 52.4        | 17,423                       | 52.8        |
| Male   | 2,720,635      | 47.6        | 15,568                       | 47.2        |

# Compare Travel Survey distribution with and without household weights

Daniel has kindly added `weights` to each row in the Travel Survey dataset, which represents household weights. In this section we compare distribution based on `trip_mode`, `stage_mode` and `sex` distribution with and without the household weights. In all the tables below, the column `raw_trip_freq` shows distribution [**without**]{.underline} and `weighted_trip_freq` [**with**]{.underline} `weights`.

>>>>

| Sex    | Population (N) | Percent (%) | Travel Survey Population (N) | Percent (%) |
|-------------|-------------|-------------|---------------------|-------------|
| Female | 2,996,444      | 52.4        | 17,423                       | 52.8        |
| Male   | 2,720,635      | 47.6        | 15,568                       | 47.2        |

# Compare Travel Survey distribution with and without individual weights

Daniel has kindly added `weights` to each row in the Travel Survey dataset, which represents individual weights. In this section we compare distribution based on `trip_mode`, `stage_mode` and `sex` distribution with and without the individual weights. In all the tables below, the column `raw_trip_freq` shows distribution [**without**]{.underline} and `weighted_trip_freq` [**with**]{.underline} `weights`.
